Avancement du stage

### 2025-05-12 presentation.qmd
MAJ CHARGEMENT SLIDE

# 1. Effet de μ
for mu in mu_values:
    y = genextreme.pdf(x, c=-0.1, loc=mu, scale=2)
    axes[0].plot(x, y, label=f"$\\mu$ = {mu}")
axes[0].set_title("Effet de $\\mu$", loc='right')
axes[0].set_xlabel("x")
axes[0].set_ylabel("Densité")
axes[0].legend(frameon=False, fontsize=9)

# 2. Effet de σ
for sigma in sigma_values:
    y = genextreme.pdf(x, c=-0.1, loc=0, scale=sigma)
    axes[1].plot(x, y, label=f"$\\sigma$ = {sigma}")
axes[1].set_title("Effet de $\\sigma$", loc='right')
axes[1].set_xlabel("x")
axes[1].legend(frameon=False, fontsize=9)

# 3. Effet de ξ
for xi in xi_values:
    y = genextreme.pdf(x, c=-xi, loc=0, scale=2)
    axes[2].plot(x, y, label=f"$\\xi$ = {xi}")
axes[2].set_title("Effet de $\\xi$", loc='right')
axes[2].set_xlabel("x")
axes[2].legend(frameon=False, fontsize=9)

>>>>

# 1. Effet de μ
for mu in mu_values:
    y = genextreme.pdf(x, c=-0.1, loc=mu, scale=2)
    axes[0].plot(x, y, label=f"$\\mu$ = {mu}")
axes[0].set_title("Effet de $\\mu$ (position)", loc='right')
axes[0].set_xlabel("x")
axes[0].set_ylabel("Densité")
axes[0].legend(frameon=False, fontsize=9)

# 2. Effet de σ
for sigma in sigma_values:
    y = genextreme.pdf(x, c=-0.1, loc=0, scale=sigma)
    axes[1].plot(x, y, label=f"$\\sigma$ = {sigma}")
axes[1].set_title("Effet de $\\sigma$ (échelle)", loc='right')
axes[1].set_xlabel("x")
axes[1].legend(frameon=False, fontsize=9)

# 3. Effet de ξ
for xi in xi_values:
    y = genextreme.pdf(x, c=-xi, loc=0, scale=2)
    axes[2].plot(x, y, label=f"$\\xi$ = {xi}")
axes[2].set_title("Effet de $\\xi$ (forme)", loc='right')
axes[2].set_xlabel("x")
axes[2].legend(frameon=False, fontsize=9)
